\documentclass[../root.tex]{subfiles}

\begin{document}

\section{Implementation}

For the purpose of experimenting with the ideas presented here, we have implemented
a planning toolbox in the Python language. Our toolbox contains a (P)PDDL parser and
data structures to represent internally the domains and problems as Python classes
and manipulate them. We have also implemented a PPDDL simulator that reads problem
descriptions and simulates the probabilistic effects of actions. This simulator
has been employed to obtain the results that are presented in this section.
Our implementation is available in a public Github repositoy%
\footnote{\url{https://github.com/sprkrd/planning_tools}}.

Our tools use the Fast Forward and Fast Downward planners to solve PDDL problems.

On the one hand, we want to perform a quantitative assessment of the
determinization techniques described in Chapter~\ref{chap:determinization}. 
To do so, we resort to several problems from the IPPC 2018 (some of them already
introduced in the previous sections).
We also include some problems from our ``terrain'' domain (used to illustrate
the $\alpha$-Cost-Transition-Likelihood method) and instances of our own Imagine
domain, described in Chapter~\ref{chap:theory} and shown in Annex~\ref{chap:ppddl-model}.

On the one hand, we assess qualitatively the techniques for simplifying and limiting
the planning horizon. We use a modified version of our simulator to perform these
experiments. The modifications consist in removing all the predicates that should not
be available to the robot due to occlusions.

\section{Experiments with determinization techniques}

We have considered the following planner configurations:
\begin{itemize}
	\item \textbf{ml-ff:} Single-Outcome determinizer that selects the most likely outcome.
	Uses Fast Forward as a back-up planner.
	\item \textbf{ma-ff:} Same as the previous one, but selects the outcome that sets
	more predicates to true.
	\item \textbf{ao-ff:} All-Outcome determinizer. Uses Fast Forward as a back-up
	planner.
	\item \textbf{alph-1.0:} $ \alpha $-Cost-Transition-Likelihood Determinizer with
	$ \alpha = 1 $. Uses Fast Downward as a back-up planner, configured to run A* search
	with the CEA (Context Enhanced Additive) heuristic.
	\item \textbf{alph-0.2:} Same as previous but with $ \alpha = 0.2 $.
	\item \textbf{alph-0.1:} Same as previous but with $ \alpha = 0.1 $.
	\item \textbf{alph-0.0:} Same as previous but with $ \alpha = 0.0 $.
	\item \textbf{ho-lo-30:} Hindsight Optimizer with a wheel of size 30 and local
	state counter. Uses Fast Forward as a back-up planner.
	\item \textbf{ho-lo-15:} Same as previous but a wheel of size 15.
	\item \textbf{ho-gl-30:} Hindsight Optimizer with a wheel of size 30 and a global
	time step. Uses Fast Forward as a back-up planner.
	\item \textbf{ho-lo-15:} Same as previous but a wheel of size 15.
\end{itemize}

The experiments have been conducted as follows: for each domain we have considered
several problem instances and run all the determinizing agents executing actions
against the simulator. Every agent tries to solve 10 episodes of each problem.
The simulator accepts one action per step and then returns
the state that results from the execution of that action. All the episodes have a timeout
of 180 seconds (3 minutes).
We have compiled the
following statistics:
\begin{itemize}
	\item \textbf{S}: number of successful episodes.
	\item \textbf{C}: average cost (only for the successful episodes).
	\item \textbf{E}: time spent per episode.
\end{itemize}

The results are shown in Table~\ref{tab:results-determinization} for the IPPC 2008 problems.
The results for the Imagine and ``terrain'' domains are shown in
Table~\ref{tab:results-determinization-ours}.

\begin{table}[tbp]
\centering
\caption{Results of the experiments with the IPPC2008 domains}
\resizebox{0.8\textwidth}{!}{\begin{tabular}{|r|r|r|r|r|r|r|}
\hline
\textbf{Problem} & \multicolumn{ 3}{c|}{\textbf{ex-blocksworld}} & \multicolumn{ 3}{c|}{\textbf{zenotravel}} \\ \hline
\textbf{Determinizer} & \textbf{S} & \textbf{C} & \textbf{E} & \textbf{S} & \textbf{C} & \textbf{E} \\ \hline
\textbf{ml-ff} & 34/50 (68\%) & 9.35 & 0.02 & 20/20 (100\%) & 66.60 & 0.02 \\ \hline
\textbf{ma-ff} & 10/50 (20\%) & 5.00 & 0.03 & 20/20 (100\%) & 48.35 & 0.02 \\ \hline
\textbf{ao-ff} & 31/50 (62\%) & 9.06 & 0.02 & 20/20 (100\%) & 61.10 & 0.02 \\ \hline
\textbf{alph-1.0} & 29/50 (58\%) & 8.72 & 0.14 & 20/20 (100\%) & 59.90 & 0.15 \\ \hline
\textbf{alph-0.2} & 28/50 (56\%) & 8.07 & 0.15 & 20/20 (100\%) & 57.65 & 0.14 \\ \hline
\textbf{alph-0.1} & 34/50 (68\%) & 9.06 & 0.14 & 20/20 (100\%) & 70.35 & 0.15 \\ \hline
\textbf{alph-0.0} & 33/50 (66\%) & 8.76 & 0.13 & 20/20 (100\%) & 36.85 & 0.14 \\ \hline
\textbf{ho-lo-30} & - & - & - & - & - & - \\ \hline
\textbf{ho-lo-15} & - & - & - & - & - & - \\ \hline
\textbf{ho-gl-30} & - & - & - & - & - & - \\ \hline
\textbf{ho-gl-15} & - & - & - & - & - & - \\ \hline\hline
\textbf{Problem} & \multicolumn{ 3}{c|}{\textbf{triangle-tw}} & \multicolumn{ 3}{c|}{\textbf{rectangle-tw}} \\ \hline
\textbf{Determinizer} & \textbf{S} & \textbf{C} & \textbf{E} & \textbf{S} & \textbf{C} & \textbf{E} \\ \hline
\textbf{ml-ff} & 50/50 (100\%) & 21.28 & 0.10 & 11/30 (36.67\%) & 6.27 & 0.01 \\ \hline
\textbf{ma-ff} & 50/50 (100\%) & 21.04 & 0.09 & 16/30 (53.33\%) & 4.94 & 0.01 \\ \hline
\textbf{ao-ff} & 8/50 (16\%) & 2.25 & 0.01 & 11/30 (36.67\%) & 6.09 & 0.01 \\ \hline
\textbf{alph-1.0} & 6/50 (12\%) & 3.33 & 0.08 & 13/30 (43.33\%) & 4.46 & 0.12 \\ \hline
\textbf{alph-0.2} & 6/50 (12\%) & 2.67 & 0.07 & 9/30 (30\%) & 4.22 & 0.11 \\ \hline
\textbf{alph-0.1} & 6/50 (12\%) & 2.33 & 0.08 & 9/30 (30\%) & 4.67 & 0.12 \\ \hline
\textbf{alph-0.0} & 7/50 (14\%) & 2.29 & 0.07 & 15/30 (50\%) & 4.53 & 0.12 \\ \hline
\textbf{ho-lo-30} & 49/50 (98\%) & 20.78 & 20.01 & 30/30 (100\%) & 10.63 & 40.64 \\ \hline
\textbf{ho-lo-15} & 46/50 (92\%) & 21.30 & 8.45 & 24/30 (80\%) & 9.88 & 11.09 \\ \hline
\textbf{ho-gl-30} & 49/50 (98\%) & 21.80 & 27.74 & 27/30 (90\%) & 10.19 & 33.91 \\ \hline
\textbf{ho-gl-15} & 47/50 (94\%) & 21.26 & 17.71 & 25/30 (83.33\%) & 10.12 & 18.06 \\ \hline\hline
\textbf{Problem} & \multicolumn{ 3}{c|}{\textbf{blocksworld}} & \multicolumn{ 3}{c|}{\textbf{schedule}} \\ \hline
\textbf{Determinizer} & \textbf{S} & \textbf{C} & \textbf{E} & \textbf{S} & \textbf{C} & \textbf{E} \\ \hline
\textbf{ml-ff} & 30/30 (100\%) & 45.17 & 0.02 & 0/50 (0\%) & - & - \\ \hline
\textbf{ma-ff} & 30/30 (100\%) & 45.93 & 0.03 & 30/50 (60\%) & 24.20 & 0.02 \\ \hline
\textbf{ao-ff} & 30/30 (100\%) & 43.23 & 0.05 & 30/50 (60\%) & 23.20 & 0.02 \\ \hline
\textbf{alph-1.0} & 30/30 (100\%) & 15.40 & 0.13 & 50/50 (100\%) & 27.00 & 0.17 \\ \hline
\textbf{alph-0.2} & 30/30 (100\%) & 15.73 & 0.14 & 50/50 (100\%) & 34.14 & 0.18 \\ \hline
\textbf{alph-0.1} & 30/30 (100\%) & 15.67 & 0.13 & 50/50 (100\%) & 27.18 & 0.17 \\ \hline
\textbf{alph-0.0} & 30/30 (100\%) & 14.97 & 0.13 & 50/50 (100\%) & 30.24 & 0.17 \\ \hline
\textbf{ho-lo-30} & - & - & - & - & - & - \\ \hline
\textbf{ho-lo-15} & - & - & - & - & - & - \\ \hline
\textbf{ho-gl-30} & - & - & - & - & - & - \\ \hline
\textbf{ho-gl-15} & - & - & - & - & - & - \\ \hline
\end{tabular}}
\label{tab:results-determinization}
\end{table}

\begin{table}
\centering
\caption{Results of the experiments with the ''terrain`` and the recycling domain (``imagine'')}
\resizebox{0.8\textwidth}{!}{\begin{tabular}{|r|r|r|r|r|r|r|l|}
\hline
\textbf{Problem} & \multicolumn{ 3}{c|}{\textbf{terrain}} & \multicolumn{ 3}{c|}{\textbf{imagine}} \\ \hline
\textbf{Determinizer} & \textbf{S} & \textbf{C} & \textbf{E} & \textbf{S} & \textbf{C} & \textbf{E} \\ \hline
\textbf{ml-ff} & 21/30 (70\%) & 8.33 & 0.01 & 23/50 (46\%) & 20.30 & 0.04 \\ \hline
\textbf{ma-ff} & 10/30 (33.33\%) & 21.00 & 0.02 & 32/50 (64\%) & 21.81 & 0.06 \\ \hline
\textbf{ao-ff} & 14/30 (46.67\%) & 7.43 & 0.01 & 24/50 (48\%) & 20.29 & 0.06 \\ \hline
\textbf{alph-1.0} & 20/30 (66.67\%) & 7.80 & 0.10 & 32/50 (64\%) & 23.09 & 0.61 \\ \hline
\textbf{alph-0.2} & 21/30 (70\%) & 7.95 & 0.10 & 29/50 (58\%) & 22.90 & 0.61 \\ \hline
\textbf{alph-0.1} & 27/30 (90\%) & 10.33 & 0.11 & 35/50 (70\%) & 26.03 & 0.77 \\ \hline
\textbf{alph-0.0} & 30/30 (100\%) & 20.67 & 0.11 & 34/50 (68\%) & 22.44 & 0.65 \\ \hline
\textbf{ho-lo-30} & - & - & - & - & - & - \\ \hline
\textbf{ho-lo-15} & - & - & - & - & - & - \\ \hline
\textbf{ho-gl-30} & - & - & - & - & - & - \\ \hline
\textbf{ho-gl-15} & - & - & - & - & - & - \\ \hline
\end{tabular}}
\label{tab:results-determinization-ours}
\end{table}

One of our first observations is that there are barely results for the Hindsight Optimization
techniques. The reason is that our implementation takes too much time to select an action, and
the time out almost always triggered canceling the execution. Note that we do have results
for the two tireworld problems, and that they perform better than most of the remaining
planners. In the triangle tireworld problem, the hindsight optimizers are only outperformed
by the Single-Outcome approaches. This is the serendipitous effect of the Single-Outcome
Determinizers selecting the right outcome out of coincidence. The one using the maximum likelihood
criterion chose the worst outcome for the \texttt{move} action (the one that always
results in a flat tire) by mere chance, since both outcomes have a 50\% of probability. The same
applies to the Single-Outcome determinizer that selects the outcome with the largest number
of add effects, since both outcomes share the same number of additions. However, the Hindsight
Optimizers are the clear winners in the rectangle tireworld domain.

$ \alpha $-Cost-Transition-Likelihood exhibits very good performance in the terrain domain
and imagine domains. They have a reasonable success rate with a low enough $ \alpha $.


\section{Hierarchical planning}

We have combined all the techniques presented here to build a decision
maker capable of deciding intelligent sequences of instructions to
fully disassemble a hard drive. Fig.~\ref{fig:full-drive-disassembly}
shows a plan trace. Preliminary experiments seem promising in the sense that
the task decomposition makes sense and episodes are usually computed with success
against the simulator.

\begin{figure}[tbhp]
\centering
\begin{lstlisting}[numbers=none]
Starting...
[1.195s] Executed (grab-device)
[1.196s] Executed (flip top bottom)
[1.197s] Executed (place-device)
[1.197s] Executed (pick-tool star-sd power)
[1.198s] Executed (unscrew-power-non-stuck pcb-s4 star-sd bottom)
[1.633s] Executed (put-away-tool star-sd power)
[1.633s] Executed (pick-tool flat-sd power)
[1.634s] Executed (unscrew-power-non-stuck pcb-s0 flat-sd bottom)
[1.926s] Executed (unscrew-power-non-stuck pcb-s1 flat-sd bottom)
[2.192s] Executed (unscrew-power-non-stuck pcb-s2 flat-sd bottom)
[2.444s] Executed (unscrew-power-non-stuck pcb-s3 flat-sd bottom)
[2.676s] Executed (assert-clear pcb)
[2.677s] Executed (lever-power-high-confidence pcb pcb-a3 bottom)
[2.678s] Executed (check-removed pcb bottom)
[2.911s] Executed (put-away-tool flat-sd power)
[2.912s] Executed (grab-device)
[2.913s] Executed (flip bottom top)
[2.913s] Executed (place-device)
[2.914s] Executed (pick-tool flat-sd power)
[2.915s] Executed (unscrew-power-non-stuck lid-s0 flat-sd top)
[3.132s] Executed (assert-clear lid)
[3.133s] Executed (lever-power-medium-confidence lid lid-a0 top)
[3.134s] Executed (check-removed lid top)
[3.364s] Executed (put-away-tool flat-sd power)
[3.365s] Executed (grab-device)
[3.366s] Executed (flip top bottom)
[3.366s] Executed (place-device)
[3.367s] Executed (pick-tool star-sd power)
[3.368s] Executed (unscrew-power-non-stuck reader-s0 star-sd bottom)
[3.587s] Executed (put-away-tool star-sd power)
[3.588s] Executed (grab-device)
[3.589s] Executed (flip bottom top)
[3.589s] Executed (place-device)
[3.590s] Executed (pick-tool pliers power)
[3.591s] Executed (assert-clear reader)
[3.592s] Executed (extract-with-pliers-high-confidence reader reader-a1 top)
[3.594s] Executed (check-removed reader top)
[3.823s] Executed (put-away-tool pliers power)
[3.824s] Executed (grab-device)
[3.825s] Executed (flip top bottom)
[3.825s] Executed (assert-clear platter)
[3.826s] Executed (let-fall-down platter top bottom)
[3.827s] Executed (flip bottom top)
[3.828s] Executed (check-removed platter top)
[3.828s] Stopped after 44 step(s). Success!
\end{lstlisting}
\caption{Plan trace for the disassembly of a full hard disk.}
\label{fig:full-drive-disassembly}
\end{figure}

\IfEq{\jobname}{\detokenize{root}}{}{\printbibliography}

\end{document}